\section{Introduction}

Embedded systems encompass a wide array of commodity hardware, from low power
wearable devices, to large scale electro-mechanical systems. Network routers
are an example of a very specialized embedded device, focused on facilitating
digital communications. These routers range in size and power from small home
network routers, to the industrial level devices that make up the backbone of
the Internet. While all routers perform a common set of operations, i.e.\ the
routing and forwarding of network data, there are drastic differences in
performance, architecture, and capabilities between Core Routers and
counterparts found in enterprise and home networks.

The Internet backbone is composed of government and commercially controlled
network infrastructure, generally made up of Core and Edge routers, as well as
their communications channels. Typically edge routers differ from core routers
in their speed, capacity, and filtering capabilities, and serve to provide an
interface to the network core. In many cases edge routers previously served as
core routers, but have been replaced by newer hardware. Routers on the core are
subject to stringent performance requirements. Typical interfaces on Core
routers are now in excess of 100 Gbps, with some commodity routers, such as the
Cisco CRS-X Modular Service card capable of a 400-Gbps line-rate per slot, and
a total throughput of 12.8 Tbps for a single chassis~\cite{_cisco_????-1}. In
contrast, a typical home network likely does not exceed 100 Mbps, with an
average connection speed of 11.9Mbps according to an Akamai report in
2015~\cite{gold_u.s._2015}. 

Routers found on the backbone infrastructure are responsible for the routing,
and forwarding of network data to their destination addresses. Typically this
is by means of IP \& Ethernet protocols, but increasingly these routers are
performing more sophisticated filtering and QoS activities. Recently, this has
drawn concern from Network Neutrality advocates, and raises concerns about the
fundamental assumptions of the role of routing in IP, and other network
protocols.

The focus of this paper is on providing an embedded systems perspective for the
hardware and software capabilities available in the routers making up the
Internet Backbone.



